Papers

### 2023-03-17 papers.qmd
update accepted papers
update papers

**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, submitted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, accepted, 2022.

>>>>

**J. D. Tucker**, M. T. Martinez, and J. M. Laborde, "Dimensionality Reduction using Elastic Measures", *Stat*, accepted, 2022. [arxiv preprint](https://arxiv.org/abs/2209.04933)

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, /10.1016/j.cam.2023.115126, 2022. [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)
